A Case of Genetic Dilution in Improved Maize: Estimating Comparative Advantage of Adoption in Ethiopia

### 2022-01-27 document/slides/finalpresentation.tex

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title[Improved Seed Adoption] %optional/
{Improved Seed Adoption and Climate Change: Hybrid Maize in Ethiopia}

\author[et al]{Barriga-Cabanillas,  Chiarella, Correa, Michuda}

@@

\date[Feb 2021] % (optional)
{CGIAR-SPIA \\
February 2021}

@@

>>>>

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title[Genetic Dilution in Improved Maize] %optional/
{A Case of Genetic Dilution in Improved Maize: Estimating
Comparative Advantage of Adoption in Ethiopia}

\author[et al]{Michuda, Chiarella, Barriga-Cabanillas, Correa, }

@@

\date[January 2022] % (optional)
{CGIAR-SPIA \\
January, 2022}

@@

%---------------------------------------------------------
%---------------------------------------------------------
\begin{frame}
\frametitle{Group Random Coefficients Results}

%---------------------------------------------------------
\begin{frame}
\frametitle{Endogenous Switching Regression Results}

\input{results/tables/switch23-sr}

\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\begin{frame}
\frametitle{Discussion}

\begin{itemize}
    \item Negative returns to adoption from self-reported improved varieties.
    \item But positive returns to more genetically pure, DTMZ, CG- sourced and newer varieties.
    \item All DNA fingerprints are 70\% pure or higher. Control group has high share of false positives: no proper control. 
    \item Negative results from GRC mask a large heterogeneity in returns to adoption.
\end{itemize}
